### 2021-11-12 NSF2021/Description/specificaim1.tex
still working on SA1

\subsubsection{Problem formulation}
The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of linear
partial differential equations (PDE) and comprise hydrodynamic
interactions and hydrophobic interactions.  The formulation prevents
particle collisions through excluded volume potentials.

%\begin{wrapfigure}[h!]
\begin{wrapfigure}[9]{r}{0.55\textwidth}
  \centering
  \vspace{-20pt}
  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
  \caption{\label{fig:flow_map} A collection of amphiphilic particles
  suspended in a solvent. The solvent velocity satisfies the Stokes
  equations, and the hydrophobic forces depend on the solvent activity
  that satisfies the screened Laplace equation. The geometry is updated
  by solving the mobility problem.}
\end{wrapfigure}

The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant
solvent viscosity. The domain
$\Omega$ is the fluid region surrounding the particles.
Since the particles are rigid, the solvent velocity 
satisfies a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$
with translational velocity $\vv_i$ and
angular velocity $\omega_i$.
Given imposed forces acting on each particle,
the \emph{mobility problem} consists of finding
translational and angular velocities so that 
viscous fluid forces balance the imposed forces.

The hydrophobic interactions come from the tendency 
of particles to minimize the free energy of the structure of
the surrounding water molecules.  
Experimental measurements suggest that the free energy functional
take the form 
\begin{equation}
\label{eq:free_energy}
F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
\end{equation}
where
$u$ is an order parameter for the structure of water,
$\rho$ is a decay length,
$C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
Since waters reorient 
on a time scale much smaller than for the particle motion, 
then at each moment in time $u$ minimizes $F[u]$ and satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle motions (Figure~\ref{fig:bcs}).

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations \eqref{eq:stokes} and the
semilinear elliptic equation \eqref{eq:SL} comes from the first
variation of the energy functional.  The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces.  It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.  Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho  \left(|\nabla u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$ along the
particle boundary.
The density \eqref{eq:stress}  was first introduced
by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue of
disjoining pressure calculated by
\cite{MaRa76, ErLjCl89, KoNa15, Nagle17, KUZMIN2005}.
It is the mathematical ingredient responsible for forming particle
aggregates that sequester their hydrophobic surface regions.

By solving the above system, we obtain translational and angular
velocities of the many-body system. 
A second-order Adams-Bashforth scheme updates the particle positions and orientations.

The formulation presents a number of
mathematical and numerical challenges. For one, the domain is constantly
changing so that a new boundary value problem must be solved at each time step.
The particle boundaries are nearly touching and this requires
high-order numerical schemes to accurately calculated forces.
The domain is unbounded and there are issues with accurately
calculating the velocity in the far-field. 
Finally, the numerical routine must handle
large system sizes efficiently when their are many particles
is large.

@@

\subsubsection{Janus-particle self-assembly} 
In the linear response case,
take $f(u) = u^2$ so that water structure has its lowest potential value
at $u = 0$, representing bulk water. The solutions of \eqref{eq:SL} have
a boundary layer structure and decay to 0 in the bulk with the decay
length $\rho$. Nevertheless, a number of morphologies arise by altering
boundary conditions.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
    \end{center}
  \caption{ Self assembly with a polar boundary condition leads to
  checkboard pattern.  Green is for $u < 0$, yellow is for $u > 0$, and
  blue is for $u = 0$.
    \label{fig:self-assemblyA}}
\end{figure}
\todo{This figure is not referenced in the text.}

Consider a polar boundary condition where
$g_i(\mathbf{x}) = (\pi r)^{-1/2} \cos (\theta_i(\mathbf{x}))$
where $\theta_i$ is the angle formed by $\mathbf{x}$, the particle
center $\mathbf{a}_i$, and the particle director $\mathbf{d}_i$.
The normalization $(\pi r)^{-1/2}$ here and others below
provide for a uniform surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$
when the particles are disks of radius $r$.
The boundary condition is odd along the particle axis 
making the particle head repel the tail.
We simulate the dynamics of 100 particles with random initial position
and orientation. The particles rapidly form chains with their
directors perpendicular to the length of the chain. The equilibrium
structure consists particles positioned on a square grid
in a checkerboard pattern. This patterning is a consequence of energy
minimality and allows each particle to simultaneously
coordinate its head with that of three other particles
and its tail with that of three other particles.

\begin{figure}[h!]
\begin{center}  
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}\\
\end{center}    
\caption{With an amphiphilic boundary condition particles self-assemble
  into bilayers. The patterning shields the hydrophobic core (yellow) from the
  aqueous phase. 
      \label{fig:self-assemblyB}}
\end{figure}
\todo{This figure is not referenced in the text.}
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and are accounted for as follows.
The hydrophilic side takes the value $u = 0$ since the
apolar headgroup of a lipid, for example, does not alter the structure
of adjacent waters. The hydrophobic side takes the value $u > 0$. 
The interaction between particles is attractive. Using
$(3\pi )^{-1/2}(1 + \cos(\theta_i(\mathbf{x})))$
as a simple modification to the previous boundary condition 
produces two-dimensional micelles and bilayers \cite{Fu2018_SIAM}.
Researchers have asked us if the phenomenon is robust. To show
that it is, we use 
\begin{equation}
\label{eq:vonMises}
g_i(\mathbf{x}) =
\sqrt{
  \frac{\exp( \kappa_i(\theta_i(\mathbf{x}) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}
\end{equation}
instead where the radicand is the von Mises 
distribution with director angle $\theta^0_i$ and Bessel function
$I_0$ of order zero. The square of this function behaves as a normal
distribution with variance like $1/\kappa_i$. To replicate
experimental conditions, the concentration $\kappa_i$ and radii
$r_i$ are randomized. Using the same initial configuration, the
particles form small groups. The small groups combine to form bilayers.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
    \caption{This figure is for hydrophobic particles with a bias. The
      hydrophobic intensity is greater on one side of the particle (magenta)
      than the other (yellow).
    \label{fig:self-assemblyC}}
\end{center}
\end{figure}
\todo{This figure is not referenced in the text.}

Multilamelar bilayers arise with an increase by shifting the boundary condition
further. Let $g_i(\mathbf{x}) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\mathbf{x})))$.
This gives a hydrophobic particle with greater intensity of hydrophobicity
at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
is similar to that of the amphiphilic particle case, except that the bilayers
do not stay well separated.  Rather, the bilayers stack on top of each
other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.

@@

Here, the order parameter $u$ is the mean number of nearest
neighbors per water molecule.
The value $u_0 = 4$ gives a local minimum for the ideal
tetrahadral water network found at hydrophobic surfaces.  
The value $u_1 \sim 4.4$ gives the absolute minimum
in the bulk where there is a mixture of four and five-coordinated
waters.
When particles are well-separated, the energetic cost for filling
the interstitial region with $u_0$-phase water is prohibitive
and there is a phase shift from the $u_0$ to $u_1$ water order
---the attraction landscape is more
or less identical to the linear response theory. Conversely, when
particles are proximal, it becomes energetically favorable
to coalesce $u_0$-phases. This introduces a line tension
for the phase transition.

The equation \eqref{eq:SL} takes the form of a steady-state
Allen-Cahn equation. The Allen-Cahn equation is used in phase field
formulations of immisible fluids, for example.
PI Ryham and colaborators launched the simulation and asymptotic analysis
of phase field functionals of membrane elastic energy,
devising functionals for  
for the squared mean curvature (Willmore) energy \cite{0951-7715-18-3-016}, 
spontaneous curvature \cite{Du05} and Gaussian curvature energy \cite{DuEuler},
as well as energetic variational approaches to coupling membrane elasticity to fluids \cite{QiangDu09}.

One potential application of the Allen-Cahn-type formulation is to
explaning measured hydrophobic attraction profiles.
The experimental data on hydrophobic attraction between 
is well-established and the literature contains data for a number of
solvents and hydrocarbon species. The experimental measurements
are well-fit by a double exponential curve in the 10 to 100 nanometer range
of separation.  Below 10 nm, however, there is an amplification of force
and the attraction follows a much steeper force law not accounted
for by past phenomenoloical theories \cite{Lin2005}.

>>>>

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[10]{r}{0.55\textwidth}
  \centering
  \vspace{-12pt}
  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
  \caption{\label{fig:flow_map} A collection of amphiphilic particles
  suspended in a solvent. The solvent velocity satisfies the Stokes
  equations, and the hydrophobic forces depend on the solvent activity
  that satisfies the screened Laplace equation. The geometry is updated
  by solving the mobility problem.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of linear
partial differential equations (PDEs) and comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent, which we solve with a
second-order Adams-Bashforth method. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega$ is the fluid region surrounding the
particles. Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$. Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. Experimental measurements suggest that the free energy
functional take the form 
\begin{align*}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align*}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
\cite{MaGa13}. Since waters reorient on a time scale much smaller than
the particle motion, $u$ minimizes $F[u]$ at all time, and therefore
satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle motions (Figure~\ref{fig:bcs}).

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations \eqref{eq:stokes} and the
semilinear elliptic equation \eqref{eq:SL} comes from the first
variation of the energy functional. The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces. It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$
along the particle boundary. The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step.  The particle
boundaries are nearly touching and this requires high-order numerical
schemes to accurately calculate forces and adaptively chose an
appropriate time step size. Furthermore, there are issues with
accurately capturing the far-field boundary conditions in the unbounded
domain. Finally, the numerical routine must handle large system sizes
efficiently when their are many particles is large.

@@

\subsubsection{Janus-particle self-assembly} 
When $f(u) = u^2$, and the water structure has its lowest potential
value at $u=0$ which represents bulk water. The solutions of
\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
bulk with the decay length $\rho$. Even in this linear response case, a
number of morphologies arise by altering boundary conditions.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
    \end{center}
  \caption{\label{fig:self-assemblyA} Self-assembly with a polar
  boundary condition leads to a checkerboard pattern. Green is for $u <
  0$, yellow is for $u > 0$, and blue is for $u = 0$.}
\end{figure}

Consider a polar boundary condition where $g_i(\xx) = (\pi r)^{-1/2}
\cos (\theta_i(\xx))$ where $\theta_i$ is the angle formed by $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$. The
normalization $(\pi r)^{-1/2}$ and others below provide a uniform
surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$ for circular particles
of radius $r$. The boundary condition is odd along the particle axis
making the particle head repel the tail.  We simulate the dynamics of
100 particles with random initial position and orientation. The
particles rapidly form chains with their directors perpendicular to the
length of the chain. The equilibrium structure consists of particles
positioned on a square grid in a checkerboard pattern
(Figure~\ref{fig:self-assemblyA}. This patterning is a consequence of
energy minimality and allows each particle to simultaneously coordinate
its head with the head of three other particles and its tail with the
tail of three other particles.

\begin{figure}[h!]
\begin{center}  
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}
\end{center}    
  \caption{\label{fig:self-assemblyB} Self-assembly with with boundary
  condition that results in hydrophobic tails and hydrophilic heads. The
  resulting bilayer pattern shields the hydrophobic core (yellow) from
  the aqueous phase.}
\end{figure}
Amphiphilic particles have a hydrophobic tail and a hydrophilic head and
are accounted for as follows. The hydrophilic side takes the value $u =
0$ since the apolar head of a lipid, for example, does not alter
the structure of adjacent waters. The hydrophobic side takes the value
$u > 0$. The interaction between particles is attractive. Using $(3\pi
)^{-1/2}(1 + \cos(\theta_i(\xx)))$ as a simple modification to
the previous boundary condition produces two-dimensional micelles and
bilayers \cite{Fu2018_SIAM} (Figure~\ref{fig:self-assemblyB}).
Researchers have asked us if the phenomenon is robust. To show that it
is, we instead use the boundary condition
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}
\end{equation}
where the radicand \todo{radicand?} is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero. The
square of this function behaves as a normal distribution with variance
like $1/\kappa_i$.To replicate experimental conditions, the
concentration $\kappa_i$ and radii $r_i$ are randomized. Using the same
initial configuration, the particles form small groups that
combine to form bilayers (Figure~\ref{fig:self-assemblyC}.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
    \caption{Hydrophobic particles with a bias. The hydrophobic
    intensity is greater on one side of the particle (magenta) than the
    other (yellow).
    \label{fig:self-assemblyC}}
\end{center}
\end{figure}

Multilamelar bilayers arise with an increase by shifting the boundary condition
further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\xx)))$.
This gives a hydrophobic particle with greater intensity of hydrophobicity
at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
is similar to that of the amphiphilic particle case, except that the bilayers
do not stay well separated.  Rather, the bilayers stack on top of each
other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.

@@

Here, the order parameter $u$ is the mean number of nearest neighbors
per water molecule. The value $u_0 = 4$ gives a local minimum for the
ideal tetrahadral water network found at hydrophobic surfaces. The value
$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
mixture of four and five-coordinated waters. When particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition.

Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example. PI RR and colaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

One potential application of the Allen-Cahn-type formulation is to
explaning measured hydrophobic attraction profiles.
The experimental data on hydrophobic attraction between 
is well-established and the literature contains data for a number of
solvents and hydrocarbon species. The experimental measurements
are well-fit by a double exponential curve in the 10 to 100 nanometer range
of separation. Below 10~nm, however, there is an amplification of force
and the attraction follows a much steeper force law not accounted
for by past phenomenoloical theories~\cite{Lin2005}.
